---
title: "[Csss508a_sp18] Homework 1"
author: "Mina Ekramnia"
date: "April 3rd, 2018"
output: html_document
theme: readable
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(pander) 
library(sjPlot)
```

## Overview of the Swiss Fertility data (1988) 
This dataset provides a time demographic transition of fertility measures(Agriculture, Examination, Education, Catholic and Infant Mortality) for 47 provinces of Switzerland in the year 1888.
Here is the summary of statistics for the variables: 

```{r swiss, echo=FALSE}
pander(summary(swiss))
pander(head(swiss, 5), style = "rmarkdown", split.tables = 120)
```


## Pairwise comparison of the variables
Here we can see the joint relationships for each combination of the variables:

```{r pairwise, echo=FALSE}
pairs(swiss, col="violet", main = "Pairwise comparisons of Swiss variables")
```

## Regression Analysis

We investigate the relationship of Fertility with Education and Agriculture. Resutls are showing in graphs and statistical tables: 

Regression Fertility-Agriculture
```{r regresseion Fertility-Agriculture, echo=FALSE}
sjt.lm(lm(Fertility~Agriculture, data=swiss), show.fstat = TRUE)
sjt.lm(lm(Fertility~Education, data=swiss), show.fstat = TRUE)
```

```{r plot regression, echo=FALSE}
plot(Fertility~Agriculture, data=swiss)
plot(Fertility~Education, data=swiss)

```


As we see there is a significant relationship between education and the fertility rate in the data, as the education increases the fertility rate decreases. However, we do not see a concise pattern for the agricutlture. 